|

### 2023-03-10 paper/01-introduction.Rmd
separate files for each section

---
title: |
  Introducing STRAIN: A simple and interpretable pass rush metric inspired by materials science
short_title: STRAIN
authors: 
- name: "Author 1"
  affiliation: "Address"
  city: "City"
  country: "Country"
  email: "email1\\@example.com"
- name: "Author 2"
  affiliation: "Address2"
  city: "City2"
  country: "Country2"
  email: "email2\\@example.com"
abstract: |
  Abstract goes here
keywords: tracking data, Bornn legacy, too much Canadian
bibliography: "bibliography"
output: rticles::rss_article
header-includes:
  \usepackage{setspace}
  \usepackage{booktabs}
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)
library(here)
```

\newpage

@@

# Methods {#sec:methods}

## Data

2023 bdb [@Howard2023NFL]

first 8 weeks 2021 season

tracking: locations of players and ball, 10 fps,

pre-processing standardize

PFF scouting: pass rush role

sample restriction: remove plays w multiple QB

frames between snap and QB outcome (pass forward, sack)

sample size

## Strain rate in materials science

## Application to pass-rushing in football

# Results {#sec:results}

## Example play

```{r}
#| label: fig_field
#| fig.cap: "snapshots"
#| fig.width: 7
#| fig.height: 9
source(here("scripts", "01_fig_field.R"))
fig_field
```

Figure \ref{fig:fig_field} shows snapshots

```{r}
#| label: fig_crosby_curves
#| fig.cap: "crosby"
#| fig.width: 5
#| fig.height: 3
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

Figure \ref{fig:fig_crosby_curves} shows Crosby throughout the play

## Positional STRAIN curves

```{r}
#| label: fig_pos_curves
#| fig.cap: "STRAIN curves for different positions"
#| fig.width: 4.5
#| fig.height: 3
source(here("scripts", "03_fig_pos_curves.R"))
fig_pos_curves
```

Figure \ref{fig:fig_pos_curves} shows pos curves

## Ranking the best pass-rushers

Do we want gt tables or traditional tex table

## Corr with pressure rate = (hits + sacks + hurries) per snap

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Cor with"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

Figure \ref{fig:fig_cor_pressure} shows cor with pressure

Fairly strong correlation (r = 0.6254943) between average STRAIN & hurries + sacks + hits per snaps

## Statistical Properties of STRAIN

From @Franks2016Meta (github https://github.com/afranks86/meta-analytics)

<!--

Discrimination: Does the metric reliably differentiate between players?

Independence: Does the metric provide new information?

-->

Stability: Does the metric measure a quantity which is stable over time?  (section 5.1 of openWAR has a similar idea)

```{r}
#| label: fig_stability
#| fig.cap: "Metric stability"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

0.8544865

Figure \ref{fig:fig_stability} shows

Average STRAIN across all frames played in first and last 4 weeks

Strong correlation shows great metric stability

# Discussion {#sec:discussion}

# Acknowledgements

Big data bowl, Mike

# References

>>>>

---
output: rticles::rss_article
bibliography: bibliography.bib
---

@@

### 2023-03-10 paper/02-methods.Rmd
separate files for each section

---
title: |
  Introducing STRAIN: A simple and interpretable pass rush metric inspired by materials science
short_title: STRAIN
authors: 
- name: "Author 1"
  affiliation: "Address"
  city: "City"
  country: "Country"
  email: "email1\\@example.com"
- name: "Author 2"
  affiliation: "Address2"
  city: "City2"
  country: "Country2"
  email: "email2\\@example.com"
abstract: |
  Abstract goes here
keywords: tracking data, Bornn legacy, too much Canadian
bibliography: "bibliography"
output: rticles::rss_article
header-includes:
  \usepackage{setspace}
  \usepackage{booktabs}
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)
library(here)
```

\newpage

# Introduction {#sec:introduction}

<!--
TODO: update citations after they're published
-->

<!--
textual citation (\citet): @Baumer2023Big
parenthetical citation (\citep): [@Baumer2023Big]
-->

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool in sports analytics.
Numerous sports have been collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This spatio-temporal multi-resolution source of data have provided exceptional opportunities for researchers to perform advanced studies at a more complex level to deepen the understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

The National Football League (NFL) introduced their player tracking system known as Next Gen Stats (NGS) in 2016
BDB
https://operations.nfl.com/gameday/technology/nfl-next-gen-stats/

Previous research bdb
this year: linemen
Importance of D-linemen, pass rush (Maybe talk about role of each position, edge vs interior, defensive formation)

## Previous Pass Rush Metrics

Limitations

\begin{table}
\caption{A summary of previously-existed pass rush metrics. \label{tab:metrics}}
\centering
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Description}\\
\midrule
Sacks & a\\
Hits & a\\
Hurries & a\\
QB Pressures & a\\
Pass-Rush Productivity (PRP) & a\\
Time In Pocket (TIP) & a\\
Pass Rush Win Rate (PRWR) & Rate at which pass rusher beats pass block within 2.5 seconds after snap\\
\bottomrule
\end{tabular}
\end{table}

Table \ref{tab:metrics}

Sacks, hits, hurries, pressures

Officially tracked by the NFL since 1982, the most well known statistic for evaluating defensive linemen on pass rushing plays is the sack, which occurs when a defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass.

https://www.pro-football-reference.com/about/advanced_stats.htm

Pressures: QB pressures (hurries + knockdowns + sack plays). Note that "sack plays" in this instance include both sacks and assists.

Hurried: Times QBs were hurried - defined as a situation when the QB is forced to throw the ball earlier than intended or is chased around/out of the pocket as the result of defensive pressure

Hit: Times QBs were hit - occurs when the QB hits the ground after a throw, not marked on a sack play

PFF's Pass-Rush Productivity (PRP)

https://www.pff.com/news/pro-signature-stats-spotlight-defensive-line

More recently metrics such as Time In Pocket (TIP) and Pass Rush Win Rate (PRWR) have also been proposed and are substantial improvements over the less sophisticated counting statistics.

Pocket Time: Number of seconds the quarterback was in the pocket between the snap of the ball and a pass or the collapse of the pocket

@Burke2018Created

https://www.espn.com/nfl/story/_/id/24892208

2.5 seconds, arbitrary

While PRWR is certainly a step in the right direction, it takes continuous data and converts it to a binary win/loss, which is generally not recommended in statistical analysis

## Contributions of STRAIN

STRAIN is the best etc.

The remainder of this paper is outlined as follows.

Section \ref{sec:methods}

Section \ref{sec:results}

Section \ref{sec:discussion}

@@

@@

# Results {#sec:results}

## Example play

```{r}
#| label: fig_field
#| fig.cap: "snapshots"
#| fig.width: 7
#| fig.height: 9
source(here("scripts", "01_fig_field.R"))
fig_field
```

Figure \ref{fig:fig_field} shows snapshots

```{r}
#| label: fig_crosby_curves
#| fig.cap: "crosby"
#| fig.width: 5
#| fig.height: 3
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

Figure \ref{fig:fig_crosby_curves} shows Crosby throughout the play

## Positional STRAIN curves

```{r}
#| label: fig_pos_curves
#| fig.cap: "STRAIN curves for different positions"
#| fig.width: 4.5
#| fig.height: 3
source(here("scripts", "03_fig_pos_curves.R"))
fig_pos_curves
```

Figure \ref{fig:fig_pos_curves} shows pos curves

## Ranking the best pass-rushers

Do we want gt tables or traditional tex table

## Corr with pressure rate = (hits + sacks + hurries) per snap

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Cor with"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

Figure \ref{fig:fig_cor_pressure} shows cor with pressure

Fairly strong correlation (r = 0.6254943) between average STRAIN & hurries + sacks + hits per snaps

## Statistical Properties of STRAIN

From @Franks2016Meta (github https://github.com/afranks86/meta-analytics)

<!--

Discrimination: Does the metric reliably differentiate between players?

Independence: Does the metric provide new information?

-->

Stability: Does the metric measure a quantity which is stable over time?  (section 5.1 of openWAR has a similar idea)

```{r}
#| label: fig_stability
#| fig.cap: "Metric stability"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

0.8544865

Figure \ref{fig:fig_stability} shows

Average STRAIN across all frames played in first and last 4 weeks

Strong correlation shows great metric stability

# Discussion {#sec:discussion}

# Acknowledgements

Big data bowl, Mike

# References

>>>>

---
output: rticles::rss_article
bibliography: bibliography.bib
---

@@

math

@@

analogy

### 2023-03-10 paper/03-results.Rmd
separate files for each section

---
title: |
  Introducing STRAIN: A simple and interpretable pass rush metric inspired by materials science
short_title: STRAIN
authors: 
- name: "Author 1"
  affiliation: "Address"
  city: "City"
  country: "Country"
  email: "email1\\@example.com"
- name: "Author 2"
  affiliation: "Address2"
  city: "City2"
  country: "Country2"
  email: "email2\\@example.com"
abstract: |
  Abstract goes here
keywords: tracking data, Bornn legacy, too much Canadian
bibliography: "bibliography"
output: rticles::rss_article
header-includes:
  \usepackage{setspace}
  \usepackage{booktabs}
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)
library(here)
```

\newpage

# Introduction {#sec:introduction}

<!--
TODO: update citations after they're published
-->

<!--
textual citation (\citet): @Baumer2023Big
parenthetical citation (\citep): [@Baumer2023Big]
-->

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool in sports analytics.
Numerous sports have been collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This spatio-temporal multi-resolution source of data have provided exceptional opportunities for researchers to perform advanced studies at a more complex level to deepen the understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

The National Football League (NFL) introduced their player tracking system known as Next Gen Stats (NGS) in 2016
BDB
https://operations.nfl.com/gameday/technology/nfl-next-gen-stats/

Previous research bdb
this year: linemen
Importance of D-linemen, pass rush (Maybe talk about role of each position, edge vs interior, defensive formation)

## Previous Pass Rush Metrics

Limitations

\begin{table}
\caption{A summary of previously-existed pass rush metrics. \label{tab:metrics}}
\centering
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Description}\\
\midrule
Sacks & a\\
Hits & a\\
Hurries & a\\
QB Pressures & a\\
Pass-Rush Productivity (PRP) & a\\
Time In Pocket (TIP) & a\\
Pass Rush Win Rate (PRWR) & Rate at which pass rusher beats pass block within 2.5 seconds after snap\\
\bottomrule
\end{tabular}
\end{table}

Table \ref{tab:metrics}

Sacks, hits, hurries, pressures

Officially tracked by the NFL since 1982, the most well known statistic for evaluating defensive linemen on pass rushing plays is the sack, which occurs when a defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass.

https://www.pro-football-reference.com/about/advanced_stats.htm

Pressures: QB pressures (hurries + knockdowns + sack plays). Note that "sack plays" in this instance include both sacks and assists.

Hurried: Times QBs were hurried - defined as a situation when the QB is forced to throw the ball earlier than intended or is chased around/out of the pocket as the result of defensive pressure

Hit: Times QBs were hit - occurs when the QB hits the ground after a throw, not marked on a sack play

PFF's Pass-Rush Productivity (PRP)

https://www.pff.com/news/pro-signature-stats-spotlight-defensive-line

More recently metrics such as Time In Pocket (TIP) and Pass Rush Win Rate (PRWR) have also been proposed and are substantial improvements over the less sophisticated counting statistics.

Pocket Time: Number of seconds the quarterback was in the pocket between the snap of the ball and a pass or the collapse of the pocket

@Burke2018Created

https://www.espn.com/nfl/story/_/id/24892208

2.5 seconds, arbitrary

While PRWR is certainly a step in the right direction, it takes continuous data and converts it to a binary win/loss, which is generally not recommended in statistical analysis

## Contributions of STRAIN

STRAIN is the best etc.

The remainder of this paper is outlined as follows.

Section \ref{sec:methods}

Section \ref{sec:results}

Section \ref{sec:discussion}

# Methods {#sec:methods}

## Data

2023 bdb [@Howard2023NFL]

first 8 weeks 2021 season

tracking: locations of players and ball, 10 fps,

pre-processing standardize

PFF scouting: pass rush role

sample restriction: remove plays w multiple QB

frames between snap and QB outcome (pass forward, sack)

sample size

## Strain rate in materials science

## Application to pass-rushing in football

@@

# Discussion {#sec:discussion}

# Acknowledgements

Big data bowl, Mike

# References

>>>>

---
output: rticles::rss_article
bibliography: bibliography.bib
---

@@
